Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-11-22 manuscript.Rmd
spatial join + basic map

```{r setup, include=FALSE}
library(tidyverse)
library(sf)

travel_times <- read_csv(file = "data/washington_DC_travel_times.csv")
```

@@

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
load("data/travel_times.RData")
theme_map <- theme_void()

travel_times <- travel_times %>%
	mutate(origin_id = factor(origin_id),
				 dest_id = factor(dest_id))
```

@@

```{r join_sf}
DC_census <- st_read("data/washington_DC_censustracts.json") %>%
	select("id" = MOVEMENT_ID, geometry) %>%
	mutate(id = factor(id, levels = levels(travel_times$dest_id)))

travel_time_sf <- left_join(x = travel_times, y = DC_census, by = c("dest_id" = "id")) %>%
	st_as_sf()
```

```{r map}
travel_time_sf %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)
```
